Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-26 Docs/TODAES/paper.tex
including references and adjusting table of results

\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes
\usepackage{cite}
\usepackage{hyphenat}
\usepackage[english]{babel}
\usepackage[skip=\baselineskip]{caption}
\captionsetup[lstlisting]{font={small,tt}}

@@

\begin{table*}[t]
  \centering
  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}

 &  & \textbf{CRC32} & \textbf{Patricia} & \textbf{Dijkstra} & \textbf{Clustering} & \textbf{RC6} & \textbf{Fuzzy} & \textbf{Mars} \\[0.15cm]
\cmidrule(r){3-9}

&\textbf{Nodes} &25 &21 &26 &150 &329 &261 &417\\
&\textbf{Edges} &32 &48 &69 &331 &448 &442 &600\\
&\textbf{S0} &20 &10 &20 &50 &600 &4578 &300\\

@@

\multirow{2}{*}{\textbf{Exact Solution}}
&  Hp   &  15   &  47   &  31   &  241   &  692    &  13820   &  876 \\
&  Sp   &  19   &  4   &  19   &  46   &  533    &  4231   &  297  \\

\bottomrule[1.5pt]
%ILP
\multirow{2}{*}{\textbf{ILP}}  
&  T(s)   &  2   &  1   &  2   &  649   &  1806    &  TO   &  5.42  \\
&  Hp   &  15   &  47   &  31   &  241   &  692    &  -   &  876  \\
\hline

%GA
\multirow{2}{*}{\textbf{GA}}
&  T(s)   &  7   &  7   &  9   &  340   &  2050    &  1.37   &  5000  \\
&  Error \%   &  13.3   &  0   &  29   &  1.7   &  -6.5    &  -37.6   &  -27.5  \\
\hline

%ESBMC
\multirow{2}{*}{\textbf{ESBMC}}
&  T(s)   &  31   &  362   &  292   &  3010   &  TO    &  MO   &  MO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline

%MultiCore ESBMC
\multirow{2}{*}{\textbf{ESBMC-SS}}
&  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline

%ESBMC Parallel sequential
\multirow{2}{*}{\textbf{ESBMC-PS}}
&  T(s) &  4 &  10   &  11   &  2238   &  TO    &  MO   &  MO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline

%ESBMC Parallel Binary
\multirow{2}{*}{\textbf{ESBMC-PB}}
&  T(s)   &  6   &  5   &  6   &  207   &  TO    &  MO   &  MO \\
&  Hp   &  15   &  47   &  38   &  241   &  -    &  -   &  -  \\
\hline

%vZ
\multirow{2}{*}{\textbf{ESBMC-$\nu$Z}}
&  T(s)   &  0.3   &  0.3   &  0.7   &  86.4   &  TO    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\

@@

% Bibliography
%\bibliographystyle{ACM-Reference-Format-Journals}
%\providecommand{\natexlab}[1]{#1}
%\providecommand{\url}[1]{{#1}}
%\providecommand{\urlprefix}{URL }
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi
%\providecommand{\eprint}[2][]{\url{#2}}

%1
%\bibitem{Arato2003}
%Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D. (2003), ``{Hardware/software partitioning in embedded system %design},'' In: Proc. of the Intl. Symp. of Intelligent Signal Processing, pp. 192--202.

%2
%\bibitem{Mann2007}
%Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System %Design, v. 31, n. 3 pp. 241--263.

%3
%\bibitem{Trindade2015}
%Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded %systems,}'' In: Design Automation for Embedded Systems (to appear).

%4
%\bibitem{Trindade2016}
%Trindade, A. B., Ismail, H. I., Cordeiro, L. C. (2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in %Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1-4.

%5
%\bibitem{Bjorner2015}
%Bjorner, N., Phan, A-D., Fleckenstein, L. (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc. of the Intl. Conf. on %Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 194--199.

%6
%\bibitem{Tang2009}
%Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. %on Computer Science Education},'' pp. 1900--1905.

%7
%\bibitem{OpenMP1998}
%OpenMP Architecture Review Board, OpenMP C and C++
%Application Pogram Interface, Version 1.0, October 1998.
%http://www.openmp.org%

%8
%\bibitem{Cordeiro2012}
%Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: %IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.

%9
%\bibitem{Rao2009}
%Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.

%10
%\bibitem{Biere2009}
%Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of %Satisfiability, IOS Press, pp. 457–-481.

%11
%\bibitem{Armando2009}
%Armando, A., Mantovani, J., Platania, L. (2009), ``{Bounded model checking of software using SMT solvers instead of SAT %solvers},'' In: Intl. Journal on Software Tools for Technology Transfer, v. 11, n. 1, pp. 69--83.

%12
%\bibitem{Ganai2006}
%Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on %Computer-Aided Design, pp. 794-–801.

%13
%\bibitem{Ramalho2013}
%Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L. (2013), ``{SMT-Based Bounded Model Checking of C++ %Programs.},'' In: Intl. Conf. and Workshops on the Engineering of Computer-Based Systems, pp. 147--156.

%14
%\bibitem{DeMoura2008}
%De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for %the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.

%15
%\bibitem{Brummayer2009}
%Brummayer, R., Biere, A. (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc. of the Intl. %Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp. 174-–177.

%16
%\bibitem{Barrett2011}
%Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4},'' In: %Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 6806, pp. 171--177.

%17
%\bibitem{Bozzano2005}
%Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R. (2005), ``{MathSAT: Tight %integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v. 35, n. 1-3, pp. 265--293.

%18
%\bibitem{Dutertre2014}
%Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.

%19
%\bibitem{Wu2014}
%Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N. (2014), ``{Research on OpenMP model of the parallel programming %technology for homogeneous multicore DSP},'' In: Proc. of the Intl. Conf. on Software Engineering and Service Science, pp. %921--924.

%20
%\bibitem{Bjorner2014}
%Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic %Computation in Software Science, pp. 1--10.

%21
%\bibitem{Federica2008}
%Federica, P., Rodolfo, F., Yuqing , S., Elisa, B. (2008), {``Authorization and User Failure Resiliency for WS-BPEL business %processes''}, In: Proc. of the Intl. Conf. on Service-Oriented Computing, LNCS 5364, pp. 116--131

%22
%\bibitem{NarodytskaN}
%Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI %Conf. on Artificial Intelligence, pp. 2717--2723.

%23
%\bibitem{Barth1995}
%Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
%Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.

%24
%\bibitem{Vasco2005}
%Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, %Technical University of Lisbon, Portugal.

%25
%\bibitem{Z3API}
%Magellan, ``{Source code and documentation},''
%  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.

%26
%\bibitem{Cormem}
%Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.

%27
%\bibitem{Dagum1998}
%Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.

%28
%\bibitem{TheMathWorks2013}
%The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.

%29
%\bibitem{Tranquillo2011}
%Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.

%30
%\bibitem{Hong2010}
%Hong, L., Cai, J. (2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc. of the Intl. Conf. on Computer and Automation Engineering, pp. 185--189.

%31
%\bibitem{Cordeiro2011}
%Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.

%32
%\bibitem{Teich2012}
%Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.

%33
%\bibitem{Guthaus2001}
%Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R. (2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc. of the annual workshop on workload characterization, pp. 3--14.

%34
%\bibitem{Arato2005}
%Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.

%35
%\bibitem{Holzmann2011}
%Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.

%36
%\bibitem{Holzmann2012}
%Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.

%37
%\bibitem{Wintersteiger2009}
%Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.

%38
%\bibitem{Qawasmeh2014}
%Qawasmeh, A., Malik, A., Chapman, B. (2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc. of the Intl. Symp. on Parallel \& Distributed processing, pp. 1049--1058.

%39
%\bibitem{Pavlinovic2015}
%Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.

%40
%\bibitem{Patrick2015}
%Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.

%41
%\bibitem{Holzmann11}
%Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.

%\end{thebibliography}

@@

% Acknowledgments
\begin{acks}
The authors would like to thank Dr. Maura Turolla of Telecom
Italia for providing specifications about the application scenario.
\end{acks}

% Bibliography
%\bibliographystyle{ACM-Reference-Format-Journals}
%\bibliography{acmsmall-sample-bibfile}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

@@

\medskip

\section{This is an example of Appendix section head}

Channel-switching time is measured as the time length it takes for
motes to successfully switch from one channel to another. This
parameter impacts the maximum network throughput, because motes
cannot receive or send any packet during this period of time, and it
also affects the efficiency of toggle snooping in MMSN, where motes
need to sense through channels rapidly.

By repeating experiments 100 times, we get the average
channel-switching time of Micaz motes: 24.3 $\mu$s. We then conduct
the same experiments with different Micaz motes, as well as
experiments with the transmitter switching from Channel 11 to other
channels. In both scenarios, the channel-switching time does not have
obvious changes. (In our experiments, all values are in the range of
23.6 $\mu$s to 24.9 $\mu$s.)

\section{Appendix section head}

The primary consumer of energy in WSNs is idle listening. The key to
reduce idle listening is executing low duty-cycle on nodes. Two
primary approaches are considered in controlling duty-cycles in the
MAC layer.

>>>>

\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes
\usepackage{cite}
\usepackage{hyphenat}
\usepackage[english]{babel}
\usepackage[skip=\baselineskip]{caption}
\captionsetup[lstlisting]{font={normalsize,tt}}

@@

\begin{table*}[t]
  \centering
  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
\\
 &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
\cmidrule(r){3-9}

&\textbf{\normalsize{Nodes}} &\normalsize{25} & \normalsize{21} & \normalsize{26} & \normalsize{150} & \normalsize{329} & \normalsize{261} & \normalsize{417}\\
&\textbf{\normalsize{Edges}} &\normalsize{32} & \normalsize{48} & \normalsize{69} & \normalsize{331} & \normalsize{448} & \normalsize{442} & \normalsize{600}\\
&\textbf{\normalsize{S0}} &\normalsize{20} & \normalsize{10} & \normalsize{20} & \normalsize{50} & \normalsize{600} & \normalsize{4578} & \normalsize{300} \\

@@

\multirow{4}{*}{\textbf{\normalsize{Exact Solution}}}
& & & & & & & & & \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
& & & & & & & & & \\

\bottomrule[1.5pt]
%ILP
\multirow{4}{*}{\textbf{\normalsize{ILP}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{2}   &  \normalsize{1}  &  \normalsize{2}   &  \normalsize{649}   &  \normalsize{1806}    &  \normalsize{TO}   &  \normalsize{5.42}  \\
&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  \normalsize{876}  \\
& & & & & & & & & \\
\hline

%GA
\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{7}   &  \normalsize{7}   &  \normalsize{9}   &  \normalsize{340}   &  \normalsize{2050}    &  \normalsize{1.37}   &  \normalsize{5000}  \\
&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0}   &  \normalsize{29}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  \normalsize{-27.5}  \\
& & & & & & & & & \\
\hline

%ESBMC
\multirow{4}{*}{\textbf{\normalsize{{ESBMC}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   & \normalsize{ 31}   &  \normalsize{362}   &  \normalsize{292}   &  \normalsize{3010}   & \normalsize{ TO}    &  \normalsize{MO}   &  \normalsize{MO } \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%MultiCore ESBMC
\multirow{4}{*}{\textbf{\normalsize{{ESBMC-SS}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   & \normalsize{ 2 }  &  \normalsize{6}   &  \normalsize{7 }  &  \normalsize{1615}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%ESBMC Parallel sequential
\multirow{4}{*}{\textbf{\normalsize{ESBMC-PS}}}
& & & & & & & & & \\
&  \normalsize{T(s)} &  \normalsize{4} &  \normalsize{10}   &  \normalsize{11}   &  \normalsize{2238}   &  \normalsize{TO}    &  \normalsize{MO}   &  \normalsize{MO}  \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%ESBMC Parallel Binary
\multirow{4}{*}{\textbf{\normalsize{{ESBMC-PB}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{6}   & \normalsize{ 5}   &  \normalsize{6}   &  \normalsize{207}   &  \normalsize{TO}    & \normalsize{MO}   & \normalsize{MO} \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%vZ
\multirow{4}{*}{\textbf{\normalsize{{ESBMC-$\nu$Z}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{0.3}   & \normalsize{0.3}   &  \normalsize{0.7}   &  \normalsize{86.4}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO } \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\

@@

% Bibliography
\begin{thebibliography}{5}

\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi
\providecommand{\eprint}[2][]{\url{#2}}
\bibliographystyle{ACM-Reference-Format-Journals}

%1
\bibitem{Arato2003}
Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D. (2003), ``{Hardware/software partitioning in embedded system design},'' In: Proc. of the Intl. Symp. of Intelligent Signal Processing, pp. 192--202.

%2
\bibitem{Mann2007}
Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System Design, v. 31, n. 3 pp. 241--263.

%3
\bibitem{Trindade2015}
Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).

%4
\bibitem{Trindade2016}
Trindade, A. B., Ismail, H. I., Cordeiro, L. C. (2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1-4.

%5
\bibitem{Bjorner2015}
Bjorner, N., Phan, A-D., Fleckenstein, L. (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 194--199.

%6
\bibitem{Tang2009}
Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.

%7
\bibitem{OpenMP1998}
OpenMP Architecture Review Board, OpenMP C and C++
Application Pogram Interface, Version 1.0, October 1998.
http://www.openmp.org%

%8
\bibitem{Cordeiro2012}
Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.

%9
\bibitem{Rao2009}
Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.

%10
\bibitem{Biere2009}
Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.

%11
\bibitem{Armando2009}
Armando, A., Mantovani, J., Platania, L. (2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: Intl. Journal on Software Tools for Technology Transfer, v. 11, n. 1, pp. 69--83.

%12
\bibitem{Ganai2006}
Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design, pp. 794-–801.

%13
\bibitem{Ramalho2013}
Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L. (2013), ``{SMT-Based Bounded Model Checking of C++ Programs.},'' In: Intl. Conf. and Workshops on the Engineering of Computer-Based Systems, pp. 147--156.

%14
\bibitem{DeMoura2008}
De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.

%15
\bibitem{Brummayer2009}
Brummayer, R., Biere, A. (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp. 174-–177.

%16
\bibitem{Barrett2011}
Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 6806, pp. 171--177.

%17
\bibitem{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R. (2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v. 35, n. 1-3, pp. 265--293.

%18
\bibitem{Dutertre2014}
Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.

%19
\bibitem{Wu2014}
Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N. (2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc. of the Intl. Conf. on Software Engineering and Service Science, pp. 921--924.

%20
\bibitem{Bjorner2014}
Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.

%21
\bibitem{Federica2008}
Federica, P., Rodolfo, F., Yuqing , S., Elisa, B. (2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc. of the Intl. Conf. on Service-Oriented Computing, LNCS 5364, pp. 116--131

%22
\bibitem{NarodytskaN}
Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.

%23
\bibitem{Barth1995}
Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.

%24
\bibitem{Vasco2005}
Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.

%25
\bibitem{Z3API}
Magellan, ``{Source code and documentation},''
  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.

%26
\bibitem{Cormem}
Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.

%27
\bibitem{Dagum1998}
Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.

%28
\bibitem{TheMathWorks2013}
The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.

%29
\bibitem{Tranquillo2011}
Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.

%30
\bibitem{Hong2010}
Hong, L., Cai, J. (2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc. of the Intl. Conf. on Computer and Automation Engineering, pp. 185--189.

%31
\bibitem{Cordeiro2011}
Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.

%32
\bibitem{Teich2012}
Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.

%33
\bibitem{Guthaus2001}
Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R. (2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc. of the annual workshop on workload characterization, pp. 3--14.

%34
\bibitem{Arato2005}
Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.

%35
\bibitem{Holzmann2011}
Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.

%36
\bibitem{Holzmann2012}
Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.

%37
\bibitem{Wintersteiger2009}
Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.

%38
\bibitem{Qawasmeh2014}
Qawasmeh, A., Malik, A., Chapman, B. (2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc. of the Intl. Symp. on Parallel \& Distributed processing, pp. 1049--1058.

%39
\bibitem{Pavlinovic2015}
Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.

%40
\bibitem{Patrick2015}
Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.

%41
\bibitem{Holzmann11}
Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.

\end{thebibliography}

@@

% Acknowledgments
%\begin{acks}
%The authors would like to thank Dr. Maura Turolla of Telecom
%Italia for providing specifications about the application scenario.
%\end{acks}

% Bibliography
% Bibliography
%\bibliographystyle{ACM-Reference-Format-Journals}
%\bibliography{acmsmall-sample-bibfile}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

@@

%\medskip

%\section{This is an example of Appendix section head}

%Channel-switching time is measured as the time length it takes for
%motes to successfully switch from one channel to another. This
%parameter impacts the maximum network throughput, because motes
%cannot receive or send any packet during this period of time, and it
%also affects the efficiency of toggle snooping in MMSN, where motes
%need to sense through channels rapidly.

%By repeating experiments 100 times, we get the average
%channel-switching time of Micaz motes: 24.3 $\mu$s. We then conduct
%the same experiments with different Micaz motes, as well as
%experiments with the transmitter switching from Channel 11 to other
%channels. In both scenarios, the channel-switching time does not have
%obvious changes. (In our experiments, all values are in the range of
%23.6 $\mu$s to 24.9 $\mu$s.)

%\section{Appendix section head}

%The primary consumer of energy in WSNs is idle listening. The key to
%reduce idle listening is executing low duty-cycle on nodes. Two
%primary approaches are considered in controlling duty-cycles in the
%MAC layer.
